---
output: github_document
bibliography: references.bib
---

Welcome to R for Transport Applications. 

Comments, slide and links from the course can be found here.

## Links

- [Gecomputation with R](http://geocompr.robinlovelace.net/) [@lovelace_geocomputation_2018]
- [R for Data Science](http://r4ds.had.co.nz/) [@grolemund_r_2016-1]
- [Efficient R Programming](https://csgillespie.github.io/efficientR/) [@gillespie_efficient_2016]
- [sf](https://cran.r-project.org/web/packages/sf/vignettes/) package vignettes (see also `vignette(package = "sf")`)
- [dodgr website](https://atfutures.github.io/dodgr/) (contains vignettes)
- [tutorial by Mark Padgham](https://github.com/mpadge/r4trans-april18/blob/master/bristol.Rmd)

## Notes from day 1

```{r}
# demonstration of key.pos
library(sf)
library(spData)
plot(world["pop"])
plot(world["pop"], key.pos = 3)
# for more info see:
# https://cran.r-project.org/web/packages/sf/vignettes/sf5.html
# vignette("sf")
?sf::plot
```

Demonstration of sfc to sf conversion:

```{r}
asia = world[world$continent == "Asia", ]
asia = st_union(asia)
class(asia)
asia_df = st_sf(
  data.frame(name = "asia"),
  geometry = asia
  )
class(asia_df)
```

Reading-in data - see Chapter 6 of Geocomputation with R.

```{r}
# from a file:
u = "https://github.com/martinjc/UK-GeoJSON/blob/master/json/eurostat/sco/topo_nuts2.json"
download.file(u, "scot.geojson") # download
```

```{r, eval=FALSE}
lnd = read_sf("~/repos/Creating-maps-in-R/data/lnd.geojson")
class(lnd)
write_sf(lnd, "lnd.geojson")
saveRDS()
write_rds(lnd, "lnd.rds")
file.size("lnd.geojson") / 1e6
file.size("lnd.rds") / 1e6
plot(lnd)
library(osmdata)
q = opq(bbox = "Leeds") %>% 
  add_osm_feature("leisure", value = "park")
res = osmdata_sf(q = q)
plot(res$osm_lines$geometry)
```

In order to help improve the course in the future, please provide feedback via this online form:

https://leeds.onlinesurveys.ac.uk/r-for-transport-applications-27th-27th-apr-2018


## References
