---
output: github_document
bibliography: references.bib
---

Welcome to R for Transport Applications. 

Comments, slide and links from the course can be found here.

## Links

- [Gecomputation with R](http://geocompr.robinlovelace.net/) [@lovelace_geocomputation_2018]
- [R for Data Science](http://r4ds.had.co.nz/) [@grolemund_r_2016-1]
- [Efficient R Programming](https://csgillespie.github.io/efficientR/) [@gillespie_efficient_2016]
- [sf](https://cran.r-project.org/web/packages/sf/vignettes/) package vignettes (see also `vignette(package = "sf")`)
- [dodgr website](https://atfutures.github.io/dodgr/) (contains vignettes)
- [tutorial by Mark Padgham](https://github.com/mpadge/r4trans-april18/blob/master/bristol.Rmd)

## Notes from day 1

```{r}
# demonstration of key.pos
library(sf)
library(spData)
plot(world["pop"])
plot(world["pop"], key.pos = 3)
# for more info see:
# https://cran.r-project.org/web/packages/sf/vignettes/sf5.html
# vignette("sf")
?sf::plot
```

Demonstration of sfc to sf conversion:

```{r}
asia = world[world$continent == "Asia", ]
asia = st_union(asia)
class(asia)
asia_df = st_sf(
  data.frame(name = "asia"),
  geometry = asia
  )
class(asia_df)
```

## References
